Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization

### 2023-02-20 manuscript.Rmd
they require self citation in third person

We have proposed a workflow for preregistration called preregistration as code (PAC) elsewhere [@peikertReproducibleResearchTutorial2021].
In a PAC, researchers use computer code for the planned analysis as well as a verbal description of theory and methods for the preregistration.
This combination is facilitated by dynamic document generation, where the results of the code, such as numbers, figures, and tables, are inserted automatically into the document.
The idea is that the preregistration already contains "mock results" based on simulated or pilot data, which are replaced after the actual study data becomes available.
Such approach dissolves the distinction between the preregistration document and the final scientific report.
Instead of fundamentally separate documents, preregistration, and final report are different versions of the same underlying dynamic document.
Deviations from the preregistration can therefore be clearly (and if necessary, automatically) isolated, highlighted, and inspected using version control.
Crucially, because the preregistration contains code, it may accommodate many different data patterns, i.e., it may be exploratory.
However, while a PAC is not the extend of exploration, it is very specific about exactly how probable it is to generate evidence even when the theory does not hold (theoretical risk).
Please note that while PAC is ideally suited to reduce uncertainty about theoretical risk, other more traditional forms of preregistration are also able to advance this goal.

>>>>

A workflow for preregistration called preregistration as code (PAC) that has several beneficial properties for uncertainty reduction was proposed in [@peikertReproducibleResearchTutorial2021].
In a PAC, researchers use computer code for the planned analysis as well as a verbal description of theory and methods for the preregistration.
This combination is facilitated by dynamic document generation, where the results of the code, such as numbers, figures, and tables, are inserted automatically into the document.
The idea is that the preregistration already contains "mock results" based on simulated or pilot data, which are replaced after the actual study data becomes available.
Such approach dissolves the distinction between the preregistration document and the final scientific report.
Instead of fundamentally separate documents, preregistration, and final report are different versions of the same underlying dynamic document.
Deviations from the preregistration can therefore be clearly (and if necessary, automatically) isolated, highlighted, and inspected using version control.
Crucially, because the preregistration contains code, it may accommodate many different data patterns, i.e., it may be exploratory.
However, while a PAC is not the extend of exploration, it is very specific about exactly how probable it is to generate evidence even when the theory does not hold (theoretical risk).
Please note that while PAC is ideally suited to reduce uncertainty about theoretical risk, other more traditional forms of preregistration are also able to advance this goal.
